COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code

### 2021-07-11 2_tables.Rmd
add updated loo_main.jpeg without latex code

# Clean up labels
loo_estimates %<>% 
  dplyr::mutate(
    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
    tag = factor(
      tag, ordered = TRUE,
      levels = rev(c("Female", "Male", "Up to Secondary", 
                       "> Secondary", "<25", "25-54", "55+", "All")),
      labels = rev(c("Female", "Male", "Up to Secondary", 
                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All")))
  ) %>% 
  dplyr::select(var, m, tag, estimate)

@@

ans_loo %<>% 
  dplyr::filter(group %in% c("All", "USA", "Russia")) %>% 
  dplyr::mutate(group = plyr::mapvalues(group, from = "All", to = "All LMIC"),
                tag = cat)

>>>>

# Clean up labels
loo_estimates %<>% 
  dplyr::mutate(
    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
    tag = factor(
      tag, ordered = TRUE,
      levels = rev(c("Female", "Male", "Up to Secondary", 
                       "> Secondary", "<25", "25-54", "55+", "All")),
      labels = rev(c("Female", "Male", "Up to Secondary", 
                     "More than Secondary", "<25 yr", "25-54 yr", "55+ yr", "All")))
  ) %>% 
  dplyr::select(var, m, tag, estimate)

@@

ans_loo %<>% 
  dplyr::filter(group %in% c("All", "USA", "Russia")) %>% 
  dplyr::mutate(
    group = plyr::mapvalues(group, from = "All", to = "All LMIC"),
    cat = plyr::mapvalues(cat, from = c("$< 25$", "$25-54$", "$55 +$"),
                          to = c("<25 yr", "25-54 yr", "55+ yr")),
    tag = cat)
